Reasoning about the rigor of perl programs: \\ \large gaps, limits to understanding, and means to ameliorate

### 2024-06-23 sciperl/paper.tex
more

\subsection{100\% coverage, or: how many angels can dance upon the head of a pin?}

@@

Thankfully there is a solution which uses XS to accomplish this: \texttt{Devel::Probe}\footnote{https://metacpan.org/pod/Devel::Probe}.
There is also a more fleshed-out and generic framework called \texttt{Devel::Events}\footnote{https://metacpan.org/pod/Devel::Events}.

@@

The software industry is one of the few places aside from SoEs\footnote{State-Owned Enterprises} where a 2/3 rate of failure \cite{standish} is remotely tolerable.
This is because our field is still relatively young (and thus can afford such waste due to high profit margins) but that is changing quickly.
Programming communities that do not improve their tooling to enable writing programs with less defects will over time be out-competed by those that do.

>>>>

\subsection{Code coverage all the way down the stack}

@@

Thankfully there is a solution which uses XS to accomplish this: \texttt{Devel::Probe}\footnote{https://metacpan.org/pod/Devel::Probe}.
There is also a more fleshed-out and generic framework called \texttt{Devel::Events}\footnote{https://metacpan.org/pod/Devel::Events}.
An automatic fault injection and coverage reporter via these means has yet to be built.

@@

The software industry is one of the few places aside from SoEs\footnote{State-Owned Enterprises} where a 2/3 rate of failure \cite{standish} is remotely tolerable.
This is because our field is still relatively young (and thus can afford such waste due to high profit margins).
Such a state of affairs will not persist indefinitely.
Programming communities that do not improve their tooling to enable writing programs with less defects will over time be out-competed by those that do.
